Self Regulation Ontology Retest Analyses

### 2018-07-27 code/SRO_Retest_Analyses.Rmd
updated model paths

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
```

>>>>

```{r}
# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_noncon_model.rds')
summary(m)
```

@@

```{r}
# summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
m = readRDS('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/input/icc_by_rawfit_con_model.rds')
summary(m)
```
